### 2018-09-20 Sections/optimising_the_world.tex
Adding image cropping
indexing, proof reading

\begin{figure*}[!htbp]
	\includegraphics[width=0.6\textwidth]{traffic_optimisation}
	\captionspacefig \caption{A simple road network, where vertices represent intersections and edges represent roads. Edge weights indicate their associated travel time. The goal is for Alice and Bob to both drive home optimally, i.e minimising net commute time. Let us assume that the intersections do not delay single cars, but if they become congested (i.e more than one car simultaneously) they induce a time delay of 1 on all drivers present at the intersection. If Bob were to stay at work, and only Alice was attempting to drive home, her optimal route would be \mbox{$A\to D\to F$}, with a commute time of 2. Conversely, if Alice stayed at work and Bob was driving home, his optimal route would be \mbox{$B\to D\to G$}, also with a commute time of 2. However, if both Alice and Bob were driving home at the same time there would be congestion at intersection $D$, and their combined travel time would be 6, not the intended 4. Thus, by optimising their routes independently of one another their competition for intersection $D$ would penalise both of them by 1. On the other hand, a global optimisation would show that a more optimal routing would be for Alice to take \mbox{$A\to C\to F$} (time 2.5), with Bob remaining on \mbox{$B\to D\to G$} (time 2). This would penalise Alice by only 0.5 for taking the longer road, but both Alice and Bob would no longer be penalised at the congested intersection, reducing their collective transit time to 4.5, a saving of 1.5. Note that Alice and Bob are not only better off collectively (i.e their joint travel time), but also individually. That is, Alice making the sacrifice of taking the longer route home actually benefits her individually, with an individual saving of 0.5. In this trivial example there is only one point of conflict in the network. In general, as the number of users scales up, the distinct ways in which combinations of conflicts could emerge grows exponentially.}\label{fig:traffic_opt}
\end{figure*}

@@

\begin{figure}[!htbp]
\includegraphics[width=0.3\textwidth]{3SAT}
\captionspacefig \caption{Digital circuit for an instance of the 3-\textsc{SAT} problem, with 4 clauses acting on input variables $\{x_i\}$. Each of the OR gates is input with some combination of 3 of the input bits or their compliments (i.e with a NOT gate). Each of these is referred to as a `clause', of which there are 4 in this example, but could be any number in general. The final AND gate requires that all clauses be simultaneously satisfied in order to yield a final output of `1'. The goal of the problem is to find an input bit-string $x$ that yields an output of `1'. In general, this may require exhaustively searching over the entire space of input states via brute-force, which exhibits time-complexity exponential in the length of the bit-string and associated number of clauses. This problem is proven to be \textbf{NP}-complete. Note that the similarly-defined 2-\textsc{SAT}\index{2-SAT problem} problem (i.e clauses each contain 2 input bits) is \textbf{P}, making 3-\textsc{SAT} the simplest model to consider in the study of \textbf{NP}-complete problems. For this reason 3-\textsc{SAT} is often used as the computational model when studying \textbf{NP}-complete problems.} \label{fig:3SAT}	
\end{figure}

@@

\begin{figure}[!htbp]
\includegraphics[width=0.35\textwidth]{graph_colouring}\\
\includegraphics[width=0.35\textwidth]{four_colouring}
\captionspacefig \caption{(top) Example of a graph with 3-colouring, such that no two vertices connected by an edge share the same colour. For this particular graph, 3-colouring is optimal (in the sense that the number of colours in minimised). It can easily be seen upon inspection that no 2-colouring is possible for this graph. Thus, this graph's chromatic number is \mbox{$\chi(G)=3$}\index{Chromatic number}. (bottom) A 4-colouring of the states of France\index{Elderberries}. Any planar map such as this has a chromatic number of at most 4 -- the `four colour theorem'.}\index{Graph colouring}\index{Surrender}\label{fig:graph_colouring}	
\end{figure}

@@

\begin{figure}[!htbp]
	\includegraphics[width=0.475\textwidth]{search_tree}
	\captionspacefig \caption{A search tree\index{Search tree} is an outwardly-directed tree graph in which each vertex represents a state of the system (i.e `board position' in chess\index{Chess}). Edges represent actions (or `moves') available from the position from which the edge emanates. The root node represents the current position, and the depth of a vertex (i.e it's distance from the root node) represents its future time. A path through the tree therefore represents a sequence of moves up to some point in future time. If the tree had maximum depth, a route (from root to leaf) would represent an entire single game, and the complete set of routes would represent all possible ways in which the game can be played. A complete analysis of a complete search tree with maximum depth would therefore allow us to exhaustively analyse all possible ways in which a game could be played to completion, enabling optimal gameplay. However, since the number of vertices/edges in a tree graph grows exponentially with depth, the configuration search space in a game grows exponentially with how may moves into the future we wish to explore, thereby strongly limiting tree depth in practical implementations.}\label{fig:search_tree}
\end{figure}

>>>>

\begin{figure*}[!htbp]
	\includegraphics[clip=true, width=0.6\textwidth]{traffic_optimisation}
	\captionspacefig \caption{A simple road network, where vertices represent intersections and edges represent roads. Edge weights indicate their associated travel time. The goal is for Alice and Bob to both drive home optimally, i.e minimising net commute time. Let us assume that the intersections do not delay single cars, but if they become congested (i.e more than one car simultaneously) they induce a time delay of 1 on all drivers present at the intersection. If Bob were to stay at work, and only Alice was attempting to drive home, her optimal route would be \mbox{$A\to D\to F$}, with a commute time of 2. Conversely, if Alice stayed at work and Bob was driving home, his optimal route would be \mbox{$B\to D\to G$}, also with a commute time of 2. However, if both Alice and Bob were driving home at the same time there would be congestion at intersection $D$, and their combined travel time would be 6, not the intended 4. Thus, by optimising their routes independently of one another their competition for intersection $D$ would penalise both of them by 1. On the other hand, a global optimisation would show that a more optimal routing would be for Alice to take \mbox{$A\to C\to F$} (time 2.5), with Bob remaining on \mbox{$B\to D\to G$} (time 2). This would penalise Alice by only 0.5 for taking the longer road, but both Alice and Bob would no longer be penalised at the congested intersection, reducing their collective transit time to 4.5, a saving of 1.5. Note that Alice and Bob are not only better off collectively (i.e their joint travel time), but also individually. That is, Alice making the sacrifice of taking the longer route home actually benefits her individually, with an individual saving of 0.5. In this trivial example there is only one point of conflict in the network. In general, as the number of users scales up, the distinct ways in which combinations of conflicts could emerge grows exponentially.}\label{fig:traffic_opt}
\end{figure*}

@@

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.3\textwidth]{3SAT}
\captionspacefig \caption{Digital circuit for an instance of the 3-\textsc{SAT} problem, with 4 clauses acting on input variables $\{x_i\}$. Each of the OR gates is input with some combination of 3 of the input bits or their compliments (i.e with a NOT gate). Each of these is referred to as a `clause', of which there are 4 in this example, but could be any number in general. The final AND gate requires that all clauses be simultaneously satisfied in order to yield a final output of `1'. The goal of the problem is to find an input bit-string $x$ that yields an output of `1'. In general, this may require exhaustively searching over the entire space of input states via brute-force, which exhibits time-complexity exponential in the length of the bit-string and associated number of clauses. This problem is proven to be \textbf{NP}-complete. Note that the similarly-defined 2-\textsc{SAT}\index{2-SAT problem} problem (i.e clauses each contain 2 input bits) is \textbf{P}, making 3-\textsc{SAT} the simplest model to consider in the study of \textbf{NP}-complete problems. For this reason 3-\textsc{SAT} is often used as the computational model when studying \textbf{NP}-complete problems.} \label{fig:3SAT}	
\end{figure}

@@

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.35\textwidth]{graph_colouring}\\
\includegraphics[clip=true, width=0.35\textwidth]{four_colouring}
\captionspacefig \caption{(top) Example of a graph with 3-colouring, such that no two vertices connected by an edge share the same colour. For this particular graph, 3-colouring is optimal (in the sense that the number of colours in minimised). It can easily be seen upon inspection that no 2-colouring is possible for this graph. Thus, this graph's chromatic number is \mbox{$\chi(G)=3$}\index{Chromatic number}. (bottom) A 4-colouring of the states of France\index{Elderberries}. Any planar map such as this has a chromatic number of at most 4 -- the `four colour theorem'.}\index{Graph colouring}\index{Surrender}\label{fig:graph_colouring}	
\end{figure}

@@

\begin{figure}[!htbp]
	\includegraphics[clip=true, width=0.475\textwidth]{search_tree}
	\captionspacefig \caption{A search tree\index{Search tree} is an outwardly-directed tree graph in which each vertex represents a state of the system (i.e `board position' in chess\index{Chess}). Edges represent actions (or `moves') available from the position from which the edge emanates. The root node represents the current position, and the depth of a vertex (i.e it's distance from the root node) represents its future time. A path through the tree therefore represents a sequence of moves up to some point in future time. If the tree had maximum depth, a route (from root to leaf) would represent an entire single game, and the complete set of routes would represent all possible ways in which the game can be played. A complete analysis of a complete search tree with maximum depth would therefore allow us to exhaustively analyse all possible ways in which a game could be played to completion, enabling optimal gameplay. However, since the number of vertices/edges in a tree graph grows exponentially with depth, the configuration search space in a game grows exponentially with how many moves into the future we wish to explore, thereby strongly limiting tree depth in practical implementations.}\label{fig:search_tree}
\end{figure}

### 2018-09-20 Sections/physical_architectures_for_quantum_computing.tex
indexing, proof reading

\comment{Include some maths from Kok paper}

@@

The amplitudes $\gamma_{S,T}$ are given by,\index{Configuration amplitudes}
\begin{align}
	\gamma_{S,T} = \frac{\mathrm{Per}(U_{S,T})}{\sqrt{S_1!\dots S_m! T_1!\dots T_m!}},
\end{align}
and the associated configuration probabilities by,
\begin{align}
	P_{S,T} &= |\gamma_{S,T}|^2 \nonumber \\
	&= \frac{|\mathrm{Per}(U_{S,T})|^2}{S_1!\dots S_m! T_1!\dots T_m!}
\end{align}
where $\mathrm{Per}(\cdot)$ denotes the matrix permanent, and $U_{S,T}$ is a sub-matrix of $U$ -- the transfer matrix\index{Transfer matrix} associated with the particular input-to-output sample configuration -- obtained by taking $S_i$ copies of the $i$th row, and $T_j$ copies of the $j$th column of the linear optics unitary matrix $U$. For the purposes of the original complexity proof, the unitary is chosen randomly from the Haar-measure\footnote{The Haar-measure generalises the notion of a uniform distribution to higher-dimensional topologies than the real numbers, in this instance to the $\mathrm{SU}(n)$ group.}\index{Haar measure}, although it remains an open question as to what is the full class of unitaries that yield computationally hard problems.

@@

\subsection{Hybrid light-matter architectures} \label{sec:hybrid} \index{Hybrid light-matter architectures}

>>>>

@@

The amplitudes $\gamma_{S,T}$ are given by,\index{Configuration amplitudes}
\begin{align}
	\gamma_{S,T} = \frac{\mathrm{Per}(U_{S,T})}{\sqrt{S_1!\dots S_m! T_1!\dots T_m!}},
\end{align}
and the associated configuration probabilities by,
\begin{align}
	P_{S,T} &= |\gamma_{S,T}|^2 \nonumber \\
	&= \frac{|\mathrm{Per}(U_{S,T})|^2}{S_1!\dots S_m! T_1!\dots T_m!}
\end{align}
where $\mathrm{Per}(\cdot)$ denotes the matrix permanent, and $U_{S,T}$ is a sub-matrix of $U$ -- the transfer matrix\index{Transfer matrices} associated with the particular input-to-output sample configuration -- obtained by taking $S_i$ copies of the $i$th row, and $T_j$ copies of the $j$th column of the linear optics unitary matrix $U$. For the purposes of the original complexity proof, the unitary is chosen randomly from the Haar-measure\footnote{The Haar-measure generalises the notion of a uniform distribution to higher-dimensional topologies than the real numbers, in this instance to the $\mathrm{SU}(n)$ group.}\index{Haar measure}, although it remains an open question as to what is the full class of unitaries that yield computationally hard problems.

@@

\subsection{Hybrid light-matter architectures} \label{sec:hybrid} \index{Hybrid architectures}

### 2018-09-20 Sections/protocols_for_the_quantum_internet.tex
indexing, proof reading

Bell states, also known as Einstein-Podolsky-Rosen (EPR) pairs\index{Einstein-Podolsky-Rosen (EPR) pairs} \cite{bib:EPR35}, which are maximally-entangled 2-qubit states, are particularly useful for many applications, including quantum teleportation (Sec.~\ref{sec:teleport}), cluster state preparation (Sec.~\ref{sec:CSQC}), and entanglement swapping (Sec.~\ref{sec:swapping}). Bell states are the special case of 2-qubit cluster states, or equivalently, 2-qubit GHZ states,
\begin{align}
	\ket{\Phi^+} = \ket\psi_\mathrm{GHZ}^{(2)}.
\end{align}

@@

\begin{figure*}[!htbp]
\includegraphics[clip=true, width=\textwidth]{space_3}
\captionspacefig \caption{Quantum clock synchronisation schemes. (top) The proposal by Jozsa \& Dowling \textit{et al.} where a singlet state\index{Bell states} is shared and measured in an ensemble of qubits \cite{bib:jozsa00}. (bottom) The proposal by Lukin \& Ye \textit{et al.} where a GHZ state\index{GHZ states} is distributed between satellites to measure the frequency drift at the Heisenberg limit \cite{bib:komar14}.}
\label{fig:space_3}
\end{figure*}

>>>>

Bell states, also known as Einstein-Podolsky-Rosen (EPR) pairs\index{Bell states} \cite{bib:EPR35}, which are maximally-entangled 2-qubit states, are particularly useful for many applications, including quantum teleportation (Sec.~\ref{sec:teleport}), cluster state preparation (Sec.~\ref{sec:CSQC}), and entanglement swapping (Sec.~\ref{sec:swapping}). Bell states are the special case of 2-qubit cluster states, or equivalently, 2-qubit GHZ states,
\begin{align}
	\ket{\Phi^+} = \ket\psi_\mathrm{GHZ}^{(2)}.
\end{align}

@@

\begin{figure*}[!htbp]
\includegraphics[clip=true, width=\textwidth]{space_3}
\captionspacefig \caption{Quantum clock synchronisation schemes. (top) The proposal by Jozsa \& Dowling \textit{et al.} where a singlet state\index{Bell states} is shared and measured in an ensemble of qubits \cite{bib:jozsa00}. (bottom) The proposal by Lukin \& Ye \textit{et al.} where a GHZ state\index{Greenberger-Horne-Zeilinger (GHZ) states} is distributed between satellites to measure the frequency drift at the Heisenberg limit \cite{bib:komar14}.}
\label{fig:space_3}
\end{figure*}

### 2018-09-20 Sections/quality_of_service.tex
indexing, proof reading

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.39\textwidth]{entanglement_purification}
\captionspacefig \caption{Protocol for entanglement purification of two noisy Bell pairs (blue) into a single less noisy Bell pair. Not shown are trivial single-qubit local corrections that may need to be made, depending upon measurement outcomes.} \label{fig:ent_purif_circ}\index{Entanglement purification protocol}
\end{figure}

>>>>

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.39\textwidth]{entanglement_purification}
\captionspacefig \caption{Protocol for entanglement purification of two noisy Bell pairs (blue) into a single less noisy Bell pair. Not shown are trivial single-qubit local corrections that may need to be made, depending upon measurement outcomes.} \label{fig:ent_purif_circ}\index{Entanglement purification}
\end{figure}

### 2018-09-20 Sections/quantum_algorithms.tex
Adding image cropping
indexing, proof reading

Calculating Betti numbers exactly is known to be \textbf{PSPACE}-complete\index{PSPACE \& PSPACE-complete}\footnote{\textbf{PSPACE} is the complexity class of problems requiring polynomial memory with unbounded runtime, a class that is not classically efficient.}, and the best-known classical approximation algorithm has exponential runtime,
\begin{align}
O(2^n \log (1/\delta)),
\end{align}
for accuracy $\delta$ on $n$ data-points.

@@

\begin{figure}[!htbp]
\includegraphics[width=0.475\textwidth]{TDA_simplices_complex}
\captionspacefig \caption{(top) $k$-simplices\index{Simplex} are constructed as fully connected subsets of the data of different dimensions $k$. (bottom) A distance cutoff is applied to create edges within a scatterplot of raw data, from which the simplicial complex\index{Simplicial complex} is constructed. The shown example of a simplicial complex contains two 2-simplices (coloured triangles), and 6 1-simplices (edges). The final simplicial complex is highly dependent on the choice of cutoff $\epsilon$. In general, as $\epsilon$ is increased the complex will contain more simplices of higher dimension, since vertices will have more immediate neighbours.} \label{fig:TDA_simplex}	
\end{figure}

@@

\begin{table}[!htbp]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function TDA(dataPoints):
\begin{enumerate}
	\item Implement a Grover search on the set of data-points with set-membership oracle function,
	\begin{align}
f_\epsilon(s_k) = \left\{ \begin{matrix}
 1, & \mathrm{if}\,\,s_k\in S_k^\epsilon \\
 0, & \mathrm{otherwise}
\end{matrix}\right.,
\end{align}
which prepares the simplicial complex superposition state,
\begin{align}
\ket\psi_k^\epsilon = \frac{1}{\sqrt{|S_k^\epsilon|}} \sum_{s_k\in S_k^\epsilon} \ket{s_k},
\end{align}
	\item Using ancillary qubits, CNOT gates and a trace-out operation, prepare the simplicial complex uniform mixed state,
	\begin{align}
\hat\rho_k^\epsilon = \frac{1}{|S_k^\epsilon|} \sum_{s_k\in S_k^\epsilon} \ket{s_k}\bra{s_k},
\end{align}
	\item Perform quantum phase-estimation on the simplicial complex mixed state.
	\item \comment{To do - show how Betti numbers are calculated. Formulas.}
	\item Algorithm has runtime,
\begin{align}
O(n^5/\delta),
\end{align}
for accuracy $\delta$.
\item $\Box$
\end{enumerate}
\begin{center}
\if 2\pubmode
	\includegraphics[width=\textwidth]{TDA_circuit}
\else
	\includegraphics[width=0.6\textwidth]{TDA_circuit}
\fi
\end{center}
}
\end{mdframed}
\captionspacealg \caption{Quantum topological data analysis algorithm for calculating Betti numbers.} \label{alg:TDA}
\end{table}

@@

\begin{figure}[!htbp]
\includegraphics[width=0.3\textwidth]{galton_board}
\captionspacefig \caption{The Galton board yields a very simple classical sampling problem. Balls (red) are input at the top and allowed to fall freely through the pyramid network of pegs (grey), at which balls bounce to the left or right with 50\% probability. At the output the balls are collected into buckets, which populate according to a binomial distribution\index{Binomial distribution}. The computational problem is to produce statistically accurate samples from such a device, which classically is efficiently implemented by sampling the binomial distribution.}	\label{fig:galton_board}\index{Galton board}
\end{figure}

>>>>

Calculating Betti numbers exactly is known to be \textbf{PSPACE}-complete\index{PSPACE}\footnote{\textbf{PSPACE} is the complexity class of problems requiring polynomial memory with unbounded runtime, a class that is not classically efficient.}, and the best-known classical approximation algorithm has exponential runtime,
\begin{align}
O(2^n \log (1/\delta)),
\end{align}
for accuracy $\delta$ on $n$ data-points.

@@

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.475\textwidth]{TDA_simplices_complex}
\captionspacefig \caption{(top) $k$-simplices\index{Simplex} are constructed as fully connected subsets of the data of different dimensions $k$. (bottom) A distance cutoff is applied to create edges within a scatterplot of raw data, from which the simplicial complex\index{Simplicial complex} is constructed. The shown example of a simplicial complex contains two 2-simplices (coloured triangles), and 6 1-simplices (edges). The final simplicial complex is highly dependent on the choice of cutoff $\epsilon$. In general, as $\epsilon$ is increased the complex will contain more simplices of higher dimension, since vertices will have more immediate neighbours.} \label{fig:TDA_simplex}	
\end{figure}

@@

\begin{table}[!htbp]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function TDA(dataPoints):
\begin{enumerate}
	\item Implement a Grover search on the set of data-points with set-membership oracle function,
	\begin{align}
f_\epsilon(s_k) = \left\{ \begin{matrix}
 1, & \mathrm{if}\,\,s_k\in S_k^\epsilon \\
 0, & \mathrm{otherwise}
\end{matrix}\right.,
\end{align}
which prepares the simplicial complex superposition state,
\begin{align}
\ket\psi_k^\epsilon = \frac{1}{\sqrt{|S_k^\epsilon|}} \sum_{s_k\in S_k^\epsilon} \ket{s_k},
\end{align}
	\item Using ancillary qubits, CNOT gates and a trace-out operation, prepare the simplicial complex uniform mixed state,
	\begin{align}
\hat\rho_k^\epsilon = \frac{1}{|S_k^\epsilon|} \sum_{s_k\in S_k^\epsilon} \ket{s_k}\bra{s_k},
\end{align}
	\item Perform quantum phase-estimation on the simplicial complex mixed state.
	\item \comment{To do - show how Betti numbers are calculated. Formulas.}
	\item Algorithm has runtime,
\begin{align}
O(n^5/\delta),
\end{align}
for accuracy $\delta$.
\item $\Box$
\end{enumerate}
\begin{center}
\if 2\pubmode
	\includegraphics[clip=true, width=\textwidth]{TDA_circuit}
\else
	\includegraphics[clip=true, width=0.6\textwidth]{TDA_circuit}
\fi
\end{center}
}
\end{mdframed}
\captionspacealg \caption{Quantum topological data analysis algorithm for calculating Betti numbers.} \label{alg:TDA}
\end{table}

@@

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.3\textwidth]{galton_board}
\captionspacefig \caption{The Galton board yields a very simple classical sampling problem. Balls (red) are input at the top and allowed to fall freely through the pyramid network of pegs (grey), at which balls bounce to the left or right with 50\% probability. At the output the balls are collected into buckets, which populate according to a binomial distribution\index{Binomial distribution}. The computational problem is to produce statistically accurate samples from such a device, which classically is efficiently implemented by sampling the binomial distribution.}	\label{fig:galton_board}\index{Galton board}
\end{figure}

### 2018-09-20 Sections/quantum_channels.tex
Adding image cropping
indexing, proof reading

The Hermitian matrix $\chi$ is known as the \textit{process matrix}\index{Process matrix}, from which many other metrics of interest may be directly computed (some of which are discussed in Sec.~\ref{sec:quantum_meas_cost}).

@@

\begin{figure}[!htbp]
\includegraphics[width=0.35\textwidth]{CNOT_process}
\captionspacefig \caption{Process matrix for the CNOT gate, expressed in the Pauli basis. Colour coding: grey=0, white=$1/4$, black=$-1/4$.} \label{fig:CNOT_proc_matrix}
\end{figure}

@@

\begin{figure}[!htbp]
\includegraphics[width=0.3\textwidth]{example_graph}
\captionspacefig \caption{The network from Fig.~\ref{fig:example_routes}, with the quantum processes associated with each link. The net process associated with a route is given by the composition of each of the processes over the length of the route. For example, the route \mbox{$R_1=A\to C\to B$} induces the process \mbox{$\mathcal{E}_{R_1} = \mathcal{E}_{C\to B} \circ \mathcal{E}_{A\to C}$}.} \label{fig:example_proc_graph}
\end{figure}

@@

\begin{figure}[!htbp]
\includegraphics[width=0.35\textwidth]{remove_nodes}
\captionspacefig \caption{Removing node processes from network graphs on a trivial network with two nodes, $A$ and $B$. Each node is associated with a quantum process ($\mathcal{E}_A$ and $\mathcal{E}_B$). Similarly, each link is associated with a process ($\mathcal{E}_{A\to B}$ and $\mathcal{E}_{B\to A}$). (a) Representation where the node and link processes are shown explicitly. (b) The node processes are replaced with identity operations by replacing each link process with the composition of the link process and its target node process. Equivalently, the cost of each node process is added to the cost of \textit{every} incoming link and then eliminated. The same may be applied for attributes rather than costs. This procedure requires that all links be directed. If undirected links are present, they may simply be replaced by two directed links, one in each direction, implementing identical quantum processes each way.} \label{fig:remove_nodes}
\end{figure}

>>>>

The Hermitian matrix $\chi$ is known as the \textit{process matrix}\index{Process matrices}, from which many other metrics of interest may be directly computed (some of which are discussed in Sec.~\ref{sec:quantum_meas_cost}).

@@

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.35\textwidth]{CNOT_process}
\captionspacefig \caption{Process matrix for the CNOT gate, expressed in the Pauli basis. Colour coding: grey=0, white=$1/4$, black=$-1/4$.} \label{fig:CNOT_proc_matrix}
\end{figure}

@@

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.3\textwidth]{example_graph}
\captionspacefig \caption{The network from Fig.~\ref{fig:example_routes}, with the quantum processes associated with each link. The net process associated with a route is given by the composition of each of the processes over the length of the route. For example, the route \mbox{$R_1=A\to C\to B$} induces the process \mbox{$\mathcal{E}_{R_1} = \mathcal{E}_{C\to B} \circ \mathcal{E}_{A\to C}$}.} \label{fig:example_proc_graph}
\end{figure}

@@

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.35\textwidth]{remove_nodes}
\captionspacefig \caption{Removing node processes from network graphs on a trivial network with two nodes, $A$ and $B$. Each node is associated with a quantum process ($\mathcal{E}_A$ and $\mathcal{E}_B$). Similarly, each link is associated with a process ($\mathcal{E}_{A\to B}$ and $\mathcal{E}_{B\to A}$). (a) Representation where the node and link processes are shown explicitly. (b) The node processes are replaced with identity operations by replacing each link process with the composition of the link process and its target node process. Equivalently, the cost of each node process is added to the cost of \textit{every} incoming link and then eliminated. The same may be applied for attributes rather than costs. This procedure requires that all links be directed. If undirected links are present, they may simply be replaced by two directed links, one in each direction, implementing identical quantum processes each way.} \label{fig:remove_nodes}
\end{figure}

### 2018-09-20 Sections/the_quantum_space_race.tex
Adding image cropping
indexing, proof reading

\begin{figure}[!htbp]
\includegraphics[width=0.475\textwidth]{distance_to_horizon}
\captionspacefig \caption{Distance to the horizon $d$ (in kilometres), at altitude $h$ (in meters), and several illustrative examples with their elevations. The range for $h$ spans from sea level to roughly the height of Mount Everest, thereby covering the full range of altitudes possible for ground-based network nodes. However, using more practically realistic bounds on altitude, say on the order of 5,000-6,000m (already very optimistic!), line-of-sight distance to the horizon will be limited to be on the order of 200-250km. This limitation necessitates the use of repeater networks to enable the efficient approaches for constructing quantum communication channels that bypass this constraint imposed by the Earth's curvature.\index{Mount Everest}\index{Mont Blanc}\index{Burj Khalifa}} \label{fig:dist_hor}
\end{figure}

@@

\if 2\pubmode
\begin{figure}[!htbp]
\includegraphics[width=0.475\textwidth]{satellite_configs}
\captionspacefig \caption{Various possibilities for space-based quantum communication. (a) Satellite-to-satellite quantum communication \cite{bib:byrnes2017lorentz}. (b) Ground-to-satellite quantum communication \cite{bib:armengol08}.}
\label{fig:space_1}
\end{figure}
\else
\begin{figure*}[!htbp]
\includegraphics[width=\textwidth]{satellite_configs}
\captionspacefig \caption{Various possibilities for space-based quantum communication. (a) Satellite-to-satellite quantum communication \cite{bib:byrnes2017lorentz}. (b) Ground-to-satellite quantum communication \cite{bib:armengol08}.}
\label{fig:space_1}
\end{figure*}
\fi

@@

\begin{figure*}[!htbp]
\includegraphics[width=\textwidth]{space_4}
\captionspacefig \caption{The Chinese Micius quantum communications satellite. (a) Schematic of the satellite and ground stations used to observe the entangled photons \cite{bib:popkin17}. \comment{[TB: Took image from Science News, may need permission]. Picture is watermarked}. (b) Attenuation during entanglement distribution from \cite{bib:yin2017satellite}. (c) Fidelities achieved for teleportation of various states as marked from \cite{bib:ren2017ground}.}
\label{fig:space_4}
\end{figure*}

@@

The group at the National University of Singapore (NUS)\index{National University of Singapore (NUS)} also has taken the approach of using nano-satellites\index{Nano-satellite}, with the capability of generating correlated photon-pairs on-board \cite{bib:tang2016generation}. The nano-satellite weighs just 1.65kg and has all the components required for creating and detecting SPDC photon pairs. The nano-satellite approach greatly reduces the cost of space-launch, and the launch itself was performed by the Indian space agency \comment{What's it called}. As photon generation and detection are both on the same satellite, no quantum communications channel (to other satellites or Earth) was established in the experiment, although it demonstrated in-principle the space-worthiness of the basic hardware components.

@@

\begin{figure*}[!htbp]
\includegraphics[width=\textwidth]{space_2}
\captionspacefig \caption{Satellites employing quantum technologies from various groups across the world: Japan \cite{bib:horiuchi2015view}, Italy \cite{bib:vallone15}, Canada \cite{bib:jennewein2014qeyssat}, Singapore \cite{bib:tang2016generation}, and China \cite{bib:gibney16}. \comment{Tim: do we have figure permission for this?}}
\label{fig:space_2}
\end{figure*}

@@

\begin{figure}[!htbp]
	\includegraphics[width=0.475\textwidth]{satellite_constellation}
	\captionspacefig \caption{Satellite constellation network for bypassing line-of-sight constraints in long-distance quantum communication. Neighbouring satellites connect via line-of-sight in space, and there are a sufficient number of satellites to enable global coverage such that all points on the Earth's surface are visible to at least one satellite at any given time, giving them indirect quantum access to any other point on the globe. In this simple example, entanglement swapping between satellites shares a Bell pair between Columbia and Tasmania, enabling the teleportation of certain Columbian products\index{Benzoylmethylecgonine} from Bogot{\'a} to the dance parties featuring at \href{https://soundcloud.com/peter-rohde}{DJ Rohde's} holiday home.\index{DJ Rohde}\index{Pablo Escobar}} \label{fig:sat_constellation}\index{Satellite constellation}
\end{figure}

>>>>

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.475\textwidth]{distance_to_horizon}
\captionspacefig \caption{Distance to the horizon $d$ (in kilometres), at altitude $h$ (in meters), and several illustrative examples with their elevations. The range for $h$ spans from sea level to roughly the height of Mount Everest, thereby covering the full range of altitudes possible for ground-based network nodes. However, using more practically realistic bounds on altitude, say on the order of 5,000-6,000m (already very optimistic!), line-of-sight distance to the horizon will be limited to be on the order of 200-250km. This limitation necessitates the use of repeater networks to enable the efficient approaches for constructing quantum communication channels that bypass this constraint imposed by the Earth's curvature.\index{Mount Everest}\index{Mont Blanc}\index{Burj Khalifa}} \label{fig:dist_hor}
\end{figure}

@@

\if 2\pubmode
\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.475\textwidth]{satellite_configs}
\captionspacefig \caption{Various possibilities for space-based quantum communication. (a) Satellite-to-satellite quantum communication \cite{bib:byrnes2017lorentz}. (b) Ground-to-satellite quantum communication \cite{bib:armengol08}.}
\label{fig:space_1}
\end{figure}
\else
\begin{figure*}[!htbp]
\includegraphics[clip=true, width=\textwidth]{satellite_configs}
\captionspacefig \caption{Various possibilities for space-based quantum communication. (a) Satellite-to-satellite quantum communication \cite{bib:byrnes2017lorentz}. (b) Ground-to-satellite quantum communication \cite{bib:armengol08}.}
\label{fig:space_1}
\end{figure*}
\fi

@@

\begin{figure*}[!htbp]
\includegraphics[clip=true, width=\textwidth]{space_4}
\captionspacefig \caption{The Chinese Micius quantum communications satellite. (a) Schematic of the satellite and ground stations used to observe the entangled photons \cite{bib:popkin17}. \comment{[TB: Took image from Science News, may need permission]. Picture is watermarked}. (b) Attenuation during entanglement distribution from \cite{bib:yin2017satellite}. (c) Fidelities achieved for teleportation of various states as marked from \cite{bib:ren2017ground}.}
\label{fig:space_4}
\end{figure*}

@@

The group at the National University of Singapore (NUS)\index{National University of Singapore (NUS)} also has taken the approach of using nano-satellites\index{Nano-satellites}, with the capability of generating correlated photon-pairs on-board \cite{bib:tang2016generation}. The nano-satellite weighs just 1.65kg and has all the components required for creating and detecting SPDC photon pairs. The nano-satellite approach greatly reduces the cost of space-launch, and the launch itself was performed by the Indian space agency \comment{What's it called}. As photon generation and detection are both on the same satellite, no quantum communications channel (to other satellites or Earth) was established in the experiment, although it demonstrated in-principle the space-worthiness of the basic hardware components.

@@

\begin{figure*}[!htbp]
\includegraphics[clip=true, width=\textwidth]{space_2}
\captionspacefig \caption{Satellites employing quantum technologies from various groups across the world: Japan \cite{bib:horiuchi2015view}, Italy \cite{bib:vallone15}, Canada \cite{bib:jennewein2014qeyssat}, Singapore \cite{bib:tang2016generation}, and China \cite{bib:gibney16}. \comment{Tim: do we have figure permission for this?}}
\label{fig:space_2}
\end{figure*}

@@

\begin{figure}[!htbp]
	\includegraphics[clip=true, width=0.475\textwidth]{satellite_constellation}
	\captionspacefig \caption{Satellite constellation network for bypassing line-of-sight constraints in long-distance quantum communication. Neighbouring satellites connect via line-of-sight in space, and there are a sufficient number of satellites to enable global coverage such that all points on the Earth's surface are visible to at least one satellite at any given time, giving them indirect quantum access to any other point on the globe. In this simple example, entanglement swapping between satellites shares a Bell pair between Columbia and Tasmania, enabling the teleportation of certain Columbian products\index{Benzoylmethylecgonine} from Bogot{\'a} to the dance parties featuring at \href{https://soundcloud.com/peter-rohde}{DJ Rohde's} holiday home.\index{DJ Rohde}\index{Pablo Escobar}} \label{fig:sat_constellation}\index{Satellite constellation}
\end{figure}
